
\section{Background and Related Work}
\label{sect:background}


At a cloud cluster node providing access to multiple virtual machines, each
instance of a guest operating system runs on a virtual machine (VM), accessing
virtual hard disks represented as virtual disk image files in the host
operating system. For VM snapshot backups, file-level semantics are normally
not provided, and snapshot operations take place at the virtual device driver
level.  This meands no fine-grained file system metadata can be used to
determine the changed data.

Another issue is the sheer size of the backups. to maintain mutiple daily
uncompressed snapshots of each VM would be very expensive, even though
most of the data remains the same from day to day, and even between VMs common
software packages and operating systems mean that the amount of unique data is
much smaller. Backup systems have been developed to use content fingerprints to
identify duplicate content~\cite{venti02,Rhea2008}. Offline deduplication is
used in~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks
during idle time.  Several techniques have been proposed to speedup searching
of duplicate fingerprints. For example, the data domain method
~\cite{bottleneck08} uses  an in-memory Bloom filter and a prefetching cache
for data blocks  which may be accessed.  An improvement to this work with
parallelization is in ~\cite{MAD210,DEBAR}.  As discussed in
Section~\ref{sect:intro}, there is no dedicated resource for deduplication in
our targeted setting and low memory usage is required so that the resource
impact to other cloud services is minimized. Approximation techniques which
reduce the memory requirement at the expense of deduplication efficiency are
studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}.  In comparison, this
paper focuses on full deduplication without approximation

%%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
%At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
%represented as virtual disk image files in the host operating system.
%For VM snapshot backup, file-level semantics are normally not provided.
%Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
%%Only raw access information at disk block level are provided. 
%%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%%only a very small slice of cluster resource can be used for the backup purpose.



%%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
%Backup systems have been developed to use content fingerprints to identify duplicate
%content~\cite{venti02,Rhea2008}.
%Offline deduplication is 
%used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%%,NGmiddleware2011}.
%%Today's commercial data backup systems (e.g. from EMC and NetApp)
%%\cite{emc_avamar}\cite{datadomain_whitepaper}
%%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
%Several techniques have been proposed to speedup searching of duplicate
%fingerprints. For example, the data domain method ~\cite{bottleneck08} 
%uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
%accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%As discussed in Section~\ref{sect:intro},
%there is no dedicated resource for deduplication in our targeted setting and low memory usage
% is required so that the resource impact to other cloud services is minimized.
%%NG et al.~\cite{ NGmiddleware2011}  use
%%a related filtering technique for integrating deduplication in Linux  file system and the memory
%%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%%These are segments that share many chunk IDs with the incoming segment with high probability.
%The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
%to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%%lookup  
%In comparison, this paper focuses on  full deduplication without approximation.
%%We also take advantages of the fact that in a VM cloud environment,
%%the virtual device driver can easily keep track if  large data
%%segments have been modified using dirty bits and such information can avoid sending
%%unmodified data segments for deduplication, which significantly saves cost.



Additional inline deduplication techniques are studied in ~\cite{sparseindex09,Guo2011,idedup}. 
All of the above approaches have focused on
such inline duplicate detection in which  deduplication of an individual block  is on the critical write path.
In our work, this constraint is relaxed and 
there is a waiting time for many duplicate detection requests. This relaxation is acceptable because 
in our context, efficiently finishing the backup of VM images within a reasonable time window is more
important than optimizing individual VM block  backup requests, and by batch
processing the deduplication requests we can decrease resource usage.




\comments{
This paper considers a backup service uses the existing cluster computing resource. 
Another option is to attach  a separate backup system with deduplication
support the cluster, and  every machine can periodically transfer snapshots to
the attached backup system.
%One  weakness of this approach is communication bottleneck between a large number of machines
%in a cloud to this centralized  service.
The cost of allocating the above dedicated backup  resource can be expensive.
Since most of backup data is not used eventually, CPU and memory resource in such a backup service may 
not be fully utilized. This paper seeks for a low-cost architecture option.
}
%It should be emphasized that our approach does not  accumulate raw backup data temporarily for deduplication
%and does not require a significant amount of extra storage capacity.
%Our strategy is to perform a drity  scan to collect
% a small amount of disk space  to accumulate
%deduplicate requests along with necessary meta data, and perform actual backup after deduplicate detection completes.
  
%affecting the overall time of backup. 
