\documentclass[finalversion]{usetex-v1}
%\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage[colorlinks,linkcolor=red,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\usepackage{epsfig}
\usepackage{breakurl}
%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
%% Now actually use the newly defined style.
\urlstyle{leo}
%\linespread{1.2}
%\setlength{\parskip}{1ex}
\begin{document}
\title{foo}
\author{bar}
\date{}
\maketitle

\begin{abstract}
Virtualization has became the engine behind many cloud computing platforms.
In a virtualized computing environment, virtual machines
operate on virtual disks, so backing up user data is done by constantly 
taking snapshots of those virtual disks. Because such VM snapshots are huge in
terms of both quantity and individual sizes, snapshot storage would cost tremendous amount 
of space without deduplication.
Current snapshot deduplication is mainly done through copy-on-write 
on fixed-size disk blocks. Such solutions are fast but unable to handle the
 cross VM and inner-block data duplications. In addition, storing VM images and their snapshots
in the same storage engine reduce the underline design flexibility since these two kinds of data
have distinct access requirements.

In this paper, we first perform a large scale study in production VM clusters 
to show that cross VM data duplication is severe due to they have large amount of
common data. Then our data analysis finds out that the overall data duplication pattern follows the Zipf's law.
Base on these discoveries, we propose a snapshot storage deduplication scheme using variable-size chunking
to address the above problem efficiently.
We eliminate the majority of cross VM data duplication by pre-select
a small set of frequently seen chunks to dedup against, and we also remove
many inner-block duplication using smaller chunking granuarity and locality.
Experiment shows our design can achieve high deduplication ratio and throughput
without incuring significant overhead to the runtime VM environment.
\end{abstract}

\input{intro}
%\input{background}
\input{approach}
%\input{results}
\input{related}
%\input{conclusion}
\bibliographystyle{abbrv}
\bibliography{dedup}
\end{document}
