\begin{vitae}
\addcontentsline{toc}{chapter}{Curriculum Vit\ae}
{\small

\begin{vitaesection}{Education}
\vspace{-0.1cm}
   \item [2002 -- 2005] Master of Science in Computer Science, Tsinghua University, Beijing, China.
    
   \item [1997 -- 2001] Bachelor of Science in Electrical Engineering, Wuhan University, Wuhan, China.

\end{vitaesection}

% \begin{vitaesection}{Experience}
% \vspace{-0.1cm}
%    \item [1999 -- 2000] Graduate Research Assistant, University of California,
%     Santa Barbara.

% \end{vitaesection}

%{\bf Selected Publications}
\begin{vitaesection}{Publications}
%\vspace{-0.5cm}
\item Michael Daniel Agun, Tao Yang, Wei Zhang. ``Asynchronous Source-side Deduplication for Cloud Data Backup''. {\it To be submitted for publication}.

\item Wei Zhang, Michael Daniel Agun, Tao Yang, Hong Tang. ``VM-Centric Snapshot Deduplication for Converged Cloud Architectures''. {\it Submitted to 2014 ACM Symposium on Cloud Computing (SoCC'14)}.

\item Wei Zhang, Tao Yang, Gautham Narayanasamy, Hong Tang. ``Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage''. {\it In Proceedings of the 5th USENIX Workshop on Hot Topics in File and Storage Technologies (HotStorage'13)}, July 2013.

\item Wei Zhang, Hong Tang, Hao Jiang, Tao Yang, Xiaogang Li, Yue Zeng. ``Multi-level Selective Deduplication for VM Snapshots in Cloud Storage''. {\it In Proceedings of the 5th IEEE International Conference on Cloud Computing (CLOUD'12)}, June 2012.

\item Wen Ye, Wei Zhang, Rich Wolski. ``Simulation-Based Augmented Reality for Sensor Network Development''. {\it In Proceedings of the 5th ACM Conference on Embedded Networked Sensor Systems (SenSys'07)}, November 2007.

\item Wei Zhang, Haoxiang Lin. ``A Versatile Cryptographic File System for Linux''. {\it In Journal of Micro Computer Systems, China}, 2006.

\item Wei Zhang, Fuchun Sun. ``An Improved FCM Algorithm Based On Search Space Smoothing''. {\it In Proceedings of the 1st IASTED International Conference on Computational Intelligence (CI'05)}, July 2005.

\vspace{0.3cm}


\end{vitaesection}

}

\end{vitae}
